Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/conclusion.tex
Conclusion.

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
%We have addressed this problem through training a convolutional neural network to detect ambiguous regions from labeled data---in effect, by finding a non-linear mapping between image and segmentation data. This allows us to identify merge and split errors with better performance than existing systems. Our experiments have shown that guided proofreading has the potential to reduce the bottleneck in the analysis of large connectomics datasets. To encourage testing of our proposed architecture and replicate our experiments, we provide our framework and data as free and open research at (link omitted for review).

>>>>

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
In this paper, we have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replicate our experiments, we provide our framework and data as free and open research at (link omitted for review).

### 2016-11-15 paper/guidedproofreading_review.tex
Edited until result section
Testing plot layouts.
Review changes; minor issues.
Section 3 review.
Section 4 review.
Conclusion.

\usepackage{cvpr}
\usepackage{microtype}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

@@

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
%
Automatic cell image segmentation methods in connectomics produce merge and
split errors, which require correction through proofreading. Previous research
has identified the visual search for these errors as the bottleneck in
interactive proofreading. To aid error correction, we develop two classifiers
that automatically recommend candidate merge and splits to the user. These
classifiers use a convolutional neural network (CNN) that has been trained with
errors in automatic segmentations against expert-labeled ground truth. Our
classifiers detect potentially-erroneous regions by considering a large context
region around a segmentation boundary. Corrections can then be performed by a
user with yes/no decisions  resulting in faster correction times than previous
proofreading methods. We also present a fully-automatic mode that uses a
probability threshold to make merge/split decisions. Extensive experiments using
the automatic approach and comparing performance of novice and expert users
demonstrate that our method performs favorably agains state-of-the-art
proofreading methods on different connectomics datasets.
%
\end{abstract}

>>>>

\usepackage{cvpr}
\usepackage{microtype}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
% Include other packages here, before hyperref.

@@

\newcommand{\JT}[1]{\textcolor{blue}{JT: #1}}
\newcommand{\HP}[1]{\textcolor{red}{HP: #1}}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
%
Automatic cell image segmentation methods in connectomics produce merge and
split errors, which require correction through proofreading. Previous research
has identified the visual search for these errors as the bottleneck in
interactive proofreading. To aid error correction, we develop two classifiers
that automatically recommend candidate merge and splits to the user. These
classifiers use a convolutional neural network (CNN) that has been trained with
errors in automatic segmentations against expert-labeled ground truth. Our
classifiers detect potentially-erroneous regions by considering a large context
region around a segmentation boundary. Corrections can then be performed by a
user with yes/no decisions,  which results in faster correction times than previous
proofreading methods. We also present a fully-automatic mode that uses a
probability threshold to make merge/split decisions. Extensive experiments using
the automatic approach and comparing performance of novice and expert users
demonstrate that our method performs favorably against state-of-the-art
proofreading methods on different connectomics datasets.
%
\end{abstract}
